Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 mcmc.tex
pass over mcmc done

As proposals

For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
and uniform distribution for model change proposals.

\begin{align}
    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
\end{align}

Where $g$ is the proposal distribution and $P$ is the distribution of which we
defined using Gaussian distribution around previous state. $A$ is the
acceptance probability where we accept new proposal with $A(x \rightarrow x')$.

$P$ is the distribution of the pose and location of an object on image
$\mathcal{I}$.

One can also think of the image as an image cropped by detection
bounding box. We synthesize covariance matrix and create NZ-WHO
template $w(x)$ for particular viewpoint, focal length and CAD model.

In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
We found out that it requires good initialization to converge to local minima.

% there are several advantages that was not possible such as
% \textbf{on-the-fly} template generation and making large number of
% templates
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
 \label{fig:tuningmode}
\end{figure}

\paragraph{Initialization.}
To fine-tune continuous pose and location of object, we require strong
initialization. The initialization is a rough bounding box with small context
and viewpoint. Since most of the standard detectors does not provide viewpoint
of an object, we first run an ensemble of NZ-WHO templates to get rough
viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
start sampling proposals.

We initialize the $x$ using the result from the previous stage where
we run our ensemble or NZ-WHO templates to get rough estimate.

>>>>

This algorithm changes the current state $x$ to a new state $x'$ based
on the acceptance probability
\begin{align}
    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right).
\end{align}
We define $4$ different types of moves that can alter the state
(Fig.~\ref{fig:moves}), {\em (i)} changing the focal length $f$, {\em
  (ii)} one of the rotational pose parameters $p_i$, {\em (iii)} scale
  or translation, and {\em (iv)} CAD model index $m$. For (i) to
  (iii), we use Gaussian proposal distributions, and a uniform
  distribution over model changes for (iv).
\begin{align}
    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M),
\end{align}
where $g$ is the proposal distribution. % and $P$ is the distribution of which we
%defined using Gaussian distribution around previous state. $A$ is the
%acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
%
% One can also think of the image as an image cropped by detection
% bounding box. We synthesize covariance matrix and create NZ-WHO
% template $w(x)$ for particular viewpoint, focal length and CAD model.
% In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
% We found out that it requires good initialization to converge to
% local minima.
In practice, we run this algorithm for \scream{} iterations, keeping
the sample with the highest probability as our approximate estimate of
the MAP solution.
\scream{no idea what c is}

% there are several advantages that was not possible such as
% \textbf{on-the-fly} template generation and making large number of
% templates
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Metropolis Hastings move types (Section~\ref{sec:fine}).}
 \label{fig:moves}
\end{figure}

\paragraph{Initialization.}
Since the Metropolis-Hastings algorithm is susceptible to getting
stuck in local optima, we need a good initialiation in order to
increase the probability to find a solution that is close to the
global optima. We achieve this by first running a discrete,
pre-trained version of our algorithm (i.e., an ensemble of NZ-WHO
templates) in order to get promising candidate 2D bounding boxes and
poses to start from. We then initialize $x_0$ for each of these candidates.
